---
title: "Compare pandora and custom coverage breadth approaches for calling genes as present/absent (including the breadth approach based on comp. mapping against pandora-identified ref. genes)"
author: "Gavin Douglas"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
library(ggplot2)
library(reshape2)
library(kableExtra)
library(knitr)

distinct_21_colours <- c("#5b531d",
                          "#874bd2",
                          "#8aad00",
                          "#b03bc1",
                          "#ef8e00",
                          "#9387ff",
                          "#837200",
                          "#b7008b",
                          "#01d1bd",
                          "#ff3a88",
                          "#92d5a3",
                          "#a5102d",
                          "#016cba",
                          "#ff5b4b",
                          "#5e4298",
                          "#cbca7d",
                          "#8c2d6e",
                          "#c9a275",
                          "#fea9ff",
                          "#89374a",
                          "#ff8d8a")
```

# Compare inferred presence / absence profiles

Major caveat is that the exact gene ids differ based on the orig approach (as panaroo was rerun since running this method).

```{r read_in}
pandora_output <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/pandora_running/pandora_multisample.matrix",
                             header = TRUE, sep = "\t", row.names = 1)
rownames(pandora_output) <- gsub("\\.fa$", "", rownames(pandora_output))

breadth_out_orig <- readRDS("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/old/second_pass_panaroo_breadth_coverage/Gilliamella_and_Snodgrassella_present.rds")

# Need to fix gene names.
rownames(breadth_out_orig) <- gsub("Gilli_", "Gilliamella_", rownames(breadth_out_orig))
rownames(breadth_out_orig) <- gsub("Snod_", "Snodgrassella_", rownames(breadth_out_orig))

breadth_out_orig_0.5 <- breadth_out_orig

breadth_out_orig_0.5[breadth_out_orig_0.5 < 0.5] <- 0
breadth_out_orig_0.5[breadth_out_orig_0.5 >= 0.5] <- 1
breadth_out_orig_0.5 <- breadth_out_orig_0.5[-which(rowSums(breadth_out_orig_0.5) == 0), ]


breadth_out_rerun <- readRDS("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/map_against_pandora_ref/clean_tables/Ellegaard.2019.2020_pandora_panaroo_coverage_breadth.rds")

breadth_out_rerun_0.5 <- breadth_out_rerun

breadth_out_rerun_0.5[breadth_out_rerun_0.5 < 0.5] <- 0
breadth_out_rerun_0.5[breadth_out_rerun_0.5 >= 0.5] <- 1
breadth_out_rerun_0.5 <- breadth_out_rerun_0.5[-which(rowSums(breadth_out_rerun_0.5) == 0), ]
```


## Compare observed and expected intersect of positive calls {.tabset}

### Orig breadth vs pandora (based on overlapping non-group gene names)

```{r orig_obs_vs_pandora_obs_positives, fig.width=8, fig.height=8}

orig_vs_pandora_intersecting_nongroup <- rownames(pandora_output)[which(rownames(pandora_output) %in% rownames(breadth_out_orig_0.5))]
orig_vs_pandora_intersecting_nongroup <- orig_vs_pandora_intersecting_nongroup[-grep("group", orig_vs_pandora_intersecting_nongroup)]

obs_intersect <- c()
exp_intersect <- c()

for (SRR in colnames(pandora_output)) {
  pandora_present_calls <- which(pandora_output[orig_vs_pandora_intersecting_nongroup, SRR] == 1)
  breadth_orig_present_calls <- which(breadth_out_orig_0.5[orig_vs_pandora_intersecting_nongroup, SRR] == 1)
  obs_intersect <- c(obs_intersect, length(which(pandora_present_calls %in% breadth_orig_present_calls)))
  exp_intersect <- c(exp_intersect, length(pandora_present_calls) * (length(breadth_orig_present_calls) / length(orig_vs_pandora_intersecting_nongroup)))

  
}

plot(obs_intersect, exp_intersect, main = "Orig breadth vs pandora", xlab = "Observed intersecting positive calls", ylab = "Expected intersecting positive calls at random")
abline(b = 1, a = 0, lty = 2, lwd = 2)
```

### Orig breadth vs rerun breadth (based on overlapping non-group gene names)

```{r orig_obs_vs_rerun_obs_positives, fig.width=8, fig.height=8}

orig_vs_rerun_intersecting_nongroup <- rownames(breadth_out_rerun_0.5)[which(rownames(breadth_out_rerun_0.5) %in% rownames(breadth_out_orig_0.5))]
orig_vs_rerun_intersecting_nongroup <- orig_vs_rerun_intersecting_nongroup[-grep("group", orig_vs_rerun_intersecting_nongroup)]

obs_intersect <- c()
exp_intersect <- c()

for (SRR in colnames(breadth_out_rerun_0.5)) {
  rerun_present_calls <- which(breadth_out_rerun_0.5[orig_vs_rerun_intersecting_nongroup, SRR] == 1)
  breadth_orig_present_calls <- which(breadth_out_orig_0.5[orig_vs_rerun_intersecting_nongroup, SRR] == 1)
  obs_intersect <- c(obs_intersect, length(which(rerun_present_calls %in% breadth_orig_present_calls)))
  exp_intersect <- c(exp_intersect, length(rerun_present_calls) * (length(breadth_orig_present_calls) / length(orig_vs_rerun_intersecting_nongroup)))

  
}

plot(obs_intersect, exp_intersect, main = "Orig breadth vs rerun", xlab = "Observed intersecting positive calls", ylab = "Expected intersecting positive calls at random")
abline(b = 1, a = 0, lty = 2, lwd = 2)
```


### Rerun breadth vs pandora

```{r rerun_obs_vs_pandora_obs_positives, fig.width=8, fig.height=8}

rerun_vs_pandora_intersecting <- rownames(pandora_output)[which(rownames(pandora_output) %in% rownames(breadth_out_rerun_0.5))]

obs_intersect <- c()
exp_intersect <- c()

for (SRR in colnames(pandora_output)) {
  pandora_present_calls <- which(pandora_output[rerun_vs_pandora_intersecting, SRR] == 1)
  breadth_rerun_present_calls <- which(breadth_out_rerun_0.5[rerun_vs_pandora_intersecting, SRR] == 1)
  obs_intersect <- c(obs_intersect, length(which(pandora_present_calls %in% breadth_rerun_present_calls)))
  exp_intersect <- c(exp_intersect, length(pandora_present_calls) * (length(breadth_rerun_present_calls) / length(rerun_vs_pandora_intersecting)))

  
}

plot(obs_intersect, exp_intersect, main = "rerun breadth vs pandora", xlab = "Observed intersecting positive calls", ylab = "Expected intersecting positive calls at random")
abline(b = 1, a = 0, lty = 2, lwd = 2)
```


## Compare total numbers of positive calls per sample {.tabset}

### Orig breadth vs pandora (based on overlapping non-group gene names)

```{r orig_obs_vs_pandora_obs_total_positives, fig.width=8, fig.height=8}

plot(colSums(breadth_out_orig_0.5[orig_vs_pandora_intersecting_nongroup,
                                   colnames(pandora_output)]),
     colSums(pandora_output[orig_vs_pandora_intersecting_nongroup, ]),
     main = "orig breadth vs rerun breadth", xlab = "Breadth out orig", ylab = "Pandora out")
```

### Orig breadth vs rerun breadth (based on overlapping non-group gene names)

```{r orig_obs_vs_rerun_obs_total_positives, fig.width=8, fig.height=8}

plot(colSums(breadth_out_orig_0.5[orig_vs_rerun_intersecting_nongroup,
                                   colnames(breadth_out_rerun_0.5)]),
     colSums(breadth_out_rerun_0.5[orig_vs_rerun_intersecting_nongroup, ]),
     main = "orig breadth vs rerun breadth", xlab = "Breadth out orig", ylab = "Breadth out rerun")
```

### Rerun breadth vs pandora

```{r rerun_obs_vs_pandora_obs_total_positives, fig.width=8, fig.height=8}

plot(colSums(breadth_out_rerun_0.5[rerun_vs_pandora_intersecting,
                                   colnames(pandora_output)]),
     colSums(pandora_output[rerun_vs_pandora_intersecting, ]),
     main = "rerun breadth vs pandora", xlab = "Breadth out rerun", ylab = "Pandora")
```

## For a few samples, compare depth and coverage of genes that intersect vs those that do not {.tabset}

For **re-run** breadth approach vs pandora

```{r load_mean_depth}
mean_depth <- readRDS("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/map_against_pandora_ref/clean_tables/Ellegaard.2019.2020_pandora_panaroo_mean_depth.rds")
```

### SRR7287243

```{r one_sample_depth_compare_SRR7287243, fig.width = 10, fig.height = 6}

SRR <- "SRR7287243"

pandora_pos_genes <- rerun_vs_pandora_intersecting[which(pandora_output[rerun_vs_pandora_intersecting, SRR] == 1)]
breadth0.5_pos_genes <- rerun_vs_pandora_intersecting[which(breadth_out_rerun_0.5[rerun_vs_pandora_intersecting, SRR] == 1)]

pandora_only_genes <- pandora_pos_genes[which(! pandora_pos_genes %in% breadth0.5_pos_genes)]
breadth0.5_only_genes <- breadth0.5_pos_genes[which(! breadth0.5_pos_genes %in% pandora_pos_genes)]
both_genes <- pandora_pos_genes[which(pandora_pos_genes %in% breadth0.5_pos_genes)]

boxplot(mean_depth[pandora_only_genes, SRR], mean_depth[breadth0.5_only_genes, SRR], mean_depth[both_genes, SRR],
        main = SRR, names = c("pandora only", "breadth0.5 only", "both"), ylab = "Mean depth per site")

boxplot(breadth_out_rerun[pandora_only_genes, SRR], breadth_out_rerun[breadth0.5_only_genes, SRR], breadth_out_rerun[both_genes, SRR],
        main = SRR, names = c("pandora only", "breadth0.5 only", "both"), ylab = "Breadth of coverage")
```


### SRR10810005

```{r one_sample_depth_compare_SRR10810005, fig.width = 10, fig.height = 6}

SRR <- "SRR10810005"

pandora_pos_genes <- rerun_vs_pandora_intersecting[which(pandora_output[rerun_vs_pandora_intersecting, SRR] == 1)]
breadth0.5_pos_genes <- rerun_vs_pandora_intersecting[which(breadth_out_rerun_0.5[rerun_vs_pandora_intersecting, SRR] == 1)]

pandora_only_genes <- pandora_pos_genes[which(! pandora_pos_genes %in% breadth0.5_pos_genes)]
breadth0.5_only_genes <- breadth0.5_pos_genes[which(! breadth0.5_pos_genes %in% pandora_pos_genes)]
both_genes <- pandora_pos_genes[which(pandora_pos_genes %in% breadth0.5_pos_genes)]

boxplot(mean_depth[pandora_only_genes, SRR], mean_depth[breadth0.5_only_genes, SRR], mean_depth[both_genes, SRR],
        main = SRR, names = c("pandora only", "breadth0.5 only", "both"), ylab = "Mean depth per site")

boxplot(breadth_out_rerun[pandora_only_genes, SRR], breadth_out_rerun[breadth0.5_only_genes, SRR], breadth_out_rerun[both_genes, SRR],
        main = SRR, names = c("pandora only", "breadth0.5 only", "both"), ylab = "Breadth of coverage")
```


### SRR7287216

```{r one_sample_depth_compare_SRR7287216, fig.width = 10, fig.height = 6}

SRR <- "SRR7287216"

pandora_pos_genes <- rerun_vs_pandora_intersecting[which(pandora_output[rerun_vs_pandora_intersecting, SRR] == 1)]
breadth0.5_pos_genes <- rerun_vs_pandora_intersecting[which(breadth_out_rerun_0.5[rerun_vs_pandora_intersecting, SRR] == 1)]

pandora_only_genes <- pandora_pos_genes[which(! pandora_pos_genes %in% breadth0.5_pos_genes)]
breadth0.5_only_genes <- breadth0.5_pos_genes[which(! breadth0.5_pos_genes %in% pandora_pos_genes)]
both_genes <- pandora_pos_genes[which(pandora_pos_genes %in% breadth0.5_pos_genes)]

boxplot(mean_depth[pandora_only_genes, SRR], mean_depth[breadth0.5_only_genes, SRR], mean_depth[both_genes, SRR],
        main = SRR, names = c("pandora only", "breadth0.5 only", "both"), ylab = "Mean depth per site")

boxplot(breadth_out_rerun[pandora_only_genes, SRR], breadth_out_rerun[breadth0.5_only_genes, SRR], breadth_out_rerun[both_genes, SRR],
        main = SRR, names = c("pandora only", "breadth0.5 only", "both"), ylab = "Breadth of coverage")
```



# Check which method better identifies core genes as present {.tabset}

```{r read_core_genes}
combined_panaroo_and_core_genes <- readRDS("/data1/gdouglas/projects/honey_bee/ref_genome_pangenomes/panaroo_out_ref_only/combined_panaroo_and_core_genes.rds")
```

## Bifidobacterium {.tabset}

### Pandora

```{r Bifidobacterium_core_gene_evaluate_pandora, fig.width=6, fig.height=6}

Bifidobacterium_panaroo_core_genes <- grep("Bifidobacterium", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Bifidobacterium_panaroo_core_genes_filt <- Bifidobacterium_panaroo_core_genes[which(Bifidobacterium_panaroo_core_genes %in% rownames(pandora_output))]

plot(colSums(pandora_output[grep("Bifidobacterium", rownames(pandora_output)), ]),
     colSums(pandora_output[Bifidobacterium_panaroo_core_genes_filt, ]),
     ylim = c(0, 1200),
     xlim = c(0, 2000),
     xlab = "Total Bifidobacterium genes",
     ylab = "Total core genes identified",
     main = "pandora - Bifidobacterium")
abline(a = length(Bifidobacterium_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```

### Re-run breadth

```{r Bifidobacterium_core_gene_evaluate_breadth, fig.width=6, fig.height=6}

Bifidobacterium_panaroo_core_genes <- grep("Bifidobacterium", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Bifidobacterium_panaroo_core_genes_filt <- Bifidobacterium_panaroo_core_genes[which(Bifidobacterium_panaroo_core_genes %in% rownames(breadth_out_rerun_0.5))]

plot(colSums(breadth_out_rerun_0.5[grep("Bifidobacterium", rownames(breadth_out_rerun_0.5)), ]),
     colSums(breadth_out_rerun_0.5[Bifidobacterium_panaroo_core_genes_filt, ]),
     ylim = c(0, 1200),
     xlim = c(0, 2500),
     xlab = "Total Bifidobacterium genes",
     ylab = "Total core genes identified",
     main = "breadth - Bifidobacterium")
abline(a = length(Bifidobacterium_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```



## Firm4 {.tabset}

### Pandora

```{r Firm4_core_gene_evaluate_pandora, fig.width=6, fig.height=6}

Firm4_panaroo_core_genes <- grep("Firm4", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Firm4_panaroo_core_genes_filt <- Firm4_panaroo_core_genes[which(Firm4_panaroo_core_genes %in% rownames(pandora_output))]

plot(colSums(pandora_output[grep("Firm4", rownames(pandora_output)), ]),
     colSums(pandora_output[Firm4_panaroo_core_genes_filt, ]),
     ylim = c(0, 75),
     xlim = c(0, 1000),
     xlab = "Total Firm4 genes",
     ylab = "Total core genes identified",
     main = "pandora - Firm4")
abline(a = length(Firm4_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```

### Re-run breadth

```{r Firm4_core_gene_evaluate_breadth, fig.width=6, fig.height=6}

Firm4_panaroo_core_genes <- grep("Firm4", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Firm4_panaroo_core_genes_filt <- Firm4_panaroo_core_genes[which(Firm4_panaroo_core_genes %in% rownames(breadth_out_rerun_0.5))]

plot(colSums(breadth_out_rerun_0.5[grep("Firm4", rownames(breadth_out_rerun_0.5)), ]),
     colSums(breadth_out_rerun_0.5[Firm4_panaroo_core_genes_filt, ]),
     ylim = c(0, 75),
     xlim = c(0, 1500),
     xlab = "Total Firm4 genes",
     ylab = "Total core genes identified",
     main = "breadth - Firm4")
abline(a = length(Firm4_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```


## Firm5 {.tabset}

### Pandora

```{r Firm5_core_gene_evaluate_pandora, fig.width=6, fig.height=6}

Firm5_panaroo_core_genes <- grep("Firm5", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Firm5_panaroo_core_genes_filt <- Firm5_panaroo_core_genes[which(Firm5_panaroo_core_genes %in% rownames(pandora_output))]

plot(colSums(pandora_output[grep("Firm5", rownames(pandora_output)), ]),
     colSums(pandora_output[Firm5_panaroo_core_genes_filt, ]),
     ylim = c(0, 300),
     xlim = c(0, 3000),
     xlab = "Total Firm5 genes",
     ylab = "Total core genes identified",
     main = "pandora - Firm5")
abline(a = length(Firm5_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```

### Re-run breadth

```{r Firm5_core_gene_evaluate_breadth, fig.width=6, fig.height=6}

Firm5_panaroo_core_genes <- grep("Firm5", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Firm5_panaroo_core_genes_filt <- Firm5_panaroo_core_genes[which(Firm5_panaroo_core_genes %in% rownames(breadth_out_rerun_0.5))]

plot(colSums(breadth_out_rerun_0.5[grep("Firm5", rownames(breadth_out_rerun_0.5)), ]),
     colSums(breadth_out_rerun_0.5[Firm5_panaroo_core_genes_filt, ]),
     ylim = c(0, 300),
     xlim = c(0, 5000),
     xlab = "Total Firm5 genes",
     ylab = "Total core genes identified",
     main = "breadth - Firm5")
abline(a = length(Firm5_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```





## Gilliamella {.tabset}

### Pandora

```{r Gilliamella_core_gene_evaluate_pandora, fig.width=6, fig.height=6}

Gilliamella_panaroo_core_genes <- grep("Gilliamella", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Gilliamella_panaroo_core_genes_filt <- Gilliamella_panaroo_core_genes[which(Gilliamella_panaroo_core_genes %in% rownames(pandora_output))]

plot(colSums(pandora_output[grep("Gilliamella", rownames(pandora_output)), ]),
     colSums(pandora_output[Gilliamella_panaroo_core_genes_filt, ]),
     ylim = c(0, 1000),
     xlim = c(0, 3000),
     xlab = "Total Gilliamella genes",
     ylab = "Total core genes identified",
     main = "pandora - Gilliamella")
abline(a = length(Gilliamella_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```

### Re-run breadth

```{r Gilliamella_core_gene_evaluate_breadth, fig.width=6, fig.height=6}

Gilliamella_panaroo_core_genes <- grep("Gilliamella", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Gilliamella_panaroo_core_genes_filt <- Gilliamella_panaroo_core_genes[which(Gilliamella_panaroo_core_genes %in% rownames(breadth_out_rerun_0.5))]

plot(colSums(breadth_out_rerun_0.5[grep("Gilliamella", rownames(breadth_out_rerun_0.5)), ]),
     colSums(breadth_out_rerun_0.5[Gilliamella_panaroo_core_genes_filt, ]),
     ylim = c(0, 1000),
     xlim = c(0, 3000),
     xlab = "Total Gilliamella genes",
     ylab = "Total core genes identified",
     main = "breadth - Gilliamella")
abline(a = length(Gilliamella_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```



## Snodgrassella {.tabset}

### Pandora

```{r Snodgrassella_core_gene_evaluate_pandora, fig.width=6, fig.height=6}

Snodgrassella_panaroo_core_genes <- grep("Snodgrassella", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Snodgrassella_panaroo_core_genes_filt <- Snodgrassella_panaroo_core_genes[which(Snodgrassella_panaroo_core_genes %in% rownames(pandora_output))]

plot(colSums(pandora_output[grep("Snodgrassella", rownames(pandora_output)), ]),
     colSums(pandora_output[Snodgrassella_panaroo_core_genes_filt, ]),
     ylim = c(0, 1500),
     xlim = c(0, 3000),
     xlab = "Total Snodgrassella genes",
     ylab = "Total core genes identified",
     main = "pandora - Snodgrassella")
abline(a = length(Snodgrassella_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```

### Re-run breadth

```{r Snodgrassella_core_gene_evaluate_breadth, fig.width=6, fig.height=6}

Snodgrassella_panaroo_core_genes <- grep("Snodgrassella", combined_panaroo_and_core_genes$core_genes, value = TRUE)

Snodgrassella_panaroo_core_genes_filt <- Snodgrassella_panaroo_core_genes[which(Snodgrassella_panaroo_core_genes %in% rownames(breadth_out_rerun_0.5))]

plot(colSums(breadth_out_rerun_0.5[grep("Snodgrassella", rownames(breadth_out_rerun_0.5)), ]),
     colSums(breadth_out_rerun_0.5[Snodgrassella_panaroo_core_genes_filt, ]),
     ylim = c(0, 1500),
     xlim = c(0, 3000),
     xlab = "Total Snodgrassella genes",
     ylab = "Total core genes identified",
     main = "breadth - Snodgrassella")
abline(a = length(Snodgrassella_panaroo_core_genes), b = 0, lwd = 1, lty = 2)
```



