---
title: "Summarize clusters / modules in DISCOVER network"
author: "Gavin Douglas"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
library("reshape2")
library("ggnetwork")
library("igraph")
library("stringr")
library("DT")

source("/home/gdouglas/scripts/pangenome_working/Rscripts/functions.R")
```

# Read in all data

```{r read_in_data}
net <- readRDS(file = "/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/DISCOVER_network/Ellegaard_2019_2020_DISCOVER_cooccur_results_clustered_DBH0.3_net.rds")

net_components <- readRDS(file = "/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/DISCOVER_network/Ellegaard_2019_2020_DISCOVER_cooccur_results_clustered_DBH0.3_components.rds")

spydrpick_hits <- readRDS(file = "/data1/gdouglas/projects/honey_bee/ref_genome_pangenomes/spydrpick_hits.rds")

all_spydrpick_hits <- c(spydrpick_hits$Firm5, spydrpick_hits$Gilliamella, spydrpick_hits$Snodgrassella)

discover_output <- readRDS("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/DISCOVER_network/Ellegaard_2019_2020_DISCOVER_cooccur_results_clustered_DBH0.3.rds")
discover_output <- discover_output[, c("gene1", "gene2")]
discover_output_sort <- t(apply(discover_output, 1, sort))
rownames(discover_output) <- paste(discover_output_sort[, 1], discover_output_sort[, 2])

tested_genes <- readRDS("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/DISCOVER_network/Ellegaard_2019_2020_DISCOVER_tested_genes.rds")
tested_genes <- names(tested_genes)[which(tested_genes)]

module2KO <- read_KO_module_map("/data1/gdouglas/db/KEGG_v100.0/2021_10_04_KEGG_ko_module_links.tsv.gz",
                                min_num_funcs = 5)

pathway2KO <- read_KO_pathway_map("/data1/gdouglas/db/KEGG_v100.0/2021_10_04_KEGG_ko_pathway_links.tsv.gz",
                                  min_num_funcs = 5)

panaroo2KO <- read.table("/data1/gdouglas/projects/honey_bee/ref_genome_pangenomes/panaroo_ref_only_annot/KO_microbiota_panaroo_orthologs.tsv.gz",
                               header = FALSE, sep = "\t", stringsAsFactors = FALSE, row.names = 1)

panaroo2CAZy <- read.table("/data1/gdouglas/projects/honey_bee/ref_genome_pangenomes/panaroo_ref_only_annot/CAZy_microbiota_panaroo_orthologs.tsv.gz",
                         header = FALSE, sep = "\t", stringsAsFactors = FALSE, row.names = 1)
```

```{r read_description_files}
KO_descrip <- read.table("/data1/gdouglas/db/KEGG_v100.0/2021_10_04_KEGG_ko_descrip.tsv.gz",
                         header = FALSE, sep = "\t", stringsAsFactors = FALSE, quote = "", comment.char = "", row.names = 1)
rownames(KO_descrip) <- gsub("^ko:", "", rownames(KO_descrip))

pathway_descrip <- read.table("/data1/gdouglas/db/KEGG_v100.0/2021_10_04_KEGG_pathway_descrip.tsv.gz",
                         header = FALSE, sep = "\t", stringsAsFactors = FALSE, quote = "", comment.char = "", row.names = 1)
rownames(pathway_descrip) <- gsub("^path:map", "ko", rownames(pathway_descrip))

module_descrip <- read.table("/data1/gdouglas/db/KEGG_v100.0/2021_10_04_KEGG_module_descrip.tsv.gz",
                         header = FALSE, sep = "\t", stringsAsFactors = FALSE, quote = "", comment.char = "", row.names = 1)
rownames(module_descrip) <- gsub("^md:", "", rownames(module_descrip))


CAZy_descrip <- read.table("/data1/gdouglas/db/2021_10_14_CAZy_family_info.txt.gz",
                           header = TRUE, sep = "\t", stringsAsFactors = FALSE, quote = "", comment.char = "", row.names = 1)
```

```{r defined_functions}
get_edges_between_node_set <- function(nodes, edges) {
  
  intersecting_edges <- c()
  
  for (node in nodes) {
    intersecting_edges <- c(intersecting_edges,
                            rownames(edges)[which(edges[, 1] == node)],
                            rownames(edges)[which(edges[, 2] == node)])
  }
  
  intersecting_edges_breakdown <- table(intersecting_edges)
  
  return(names(intersecting_edges_breakdown)[which(intersecting_edges_breakdown == 2)])
  
}

determine_percent_phylotype_linked_edges <- function(edge_set, phylotype_pattern, strain_linked_hits) {
  # Get number and percent of edges that are known to be strain linked
  # (for each phylotype with at least one strain-linked genes defined)
  
  phylotype_edge_subset <- grep(x = edge_set, pattern = phylotype_pattern, value = TRUE)
  
  if (length(phylotype_edge_subset) > 0) {
    strain_linked_intersects <- length(which(phylotype_edge_subset %in% strain_linked_hits))
    strain_linked_intersects_percent <- (strain_linked_intersects / length(phylotype_edge_subset)) * 100
    return(c(strain_linked_intersects, strain_linked_intersects_percent))
  } else {
    return(c(NA, NA))
  }
}
```

# Network split up by each independent component.

```{r network_by_cluster}
net_flattened <- ggnetwork(net)
net_flattened$membership <- net_components$membership[net_flattened$name]

net_flattened_subsetted <- net_flattened
cluster2keep <- which(net_components$csize >= 5)
net_flattened_subsetted <- net_flattened_subsetted[which(net_flattened_subsetted$membership %in% cluster2keep), ] 
net_flattened_subsetted$membership <- factor(net_flattened_subsetted$membership)
diverse_col <- c("#b3398f",
                "#77bb3c",
                "#9a57ca",
                "#61c073",
                "#e26fcf",
                "#4c8832",
                "#5e6ccc",
                "#d79c30",
                "#5e93cd",
                "#c6572d",
                "#4bc2b6",
                "#d6414c",
                "#3c8861",
                "#dd4a84",
                "#b5b250",
                "#c590d3",
                "#707a32",
                "#94588e",
                "#936a2e",
                "#a24656",
                "#dd9663",
                "#e38389")

ggplot(net_flattened_subsetted, aes(x = x, y = y, xend = xend, yend = yend)) +
        geom_edges() +
        geom_nodes(aes(color = membership), size = 3) +
        scale_color_manual(values = diverse_col) +
        theme_blank()
```


# Strain-linkedness of each cluster

```{r strain_linkedness_table}
patterns_to_search <- list()
patterns_to_search[["Firm5"]] <- "Firm5.*Firm5"
patterns_to_search[["Gilliamella"]] <- "Gilliamella.*Gilliamella"
patterns_to_search[["Snodgrassella"]] <- "Snodgrassella.*Snodgrassella"

strain_link_metrics <- data.frame(matrix(NA, nrow = length(cluster2keep), ncol = 7))
colnames(strain_link_metrics) <- c("cluster_num", "Firm5_count", "Firm5_percent",
                                   "Gilliamella_count", "Gilliamella_percent", "Snodgrassella_count", "Snodgrassella_percent")

row_i <- 1

for (cluster_num in cluster2keep) {
  
  strain_link_metrics[row_i, "cluster_num"] <- cluster_num
  
  cluster_edges <- get_edges_between_node_set(nodes=names(net_components$membership[which(net_components$membership == cluster_num)]),
                                              edges=discover_output)

  for (phylotype in names(patterns_to_search)) {
    
    if (length(grep(patterns_to_search[[phylotype]], cluster_edges)) >= 0) {
    
      strain_link_metrics[row_i, grep(phylotype, colnames(strain_link_metrics))] <- determine_percent_phylotype_linked_edges(edge_set=cluster_edges,
                                                                                                                             phylotype_pattern = patterns_to_search[[phylotype]],
                                                                                                                             strain_linked_hits=spydrpick_hits[[phylotype]])
    }  
    
  }
  
  row_i <- row_i + 1
  
}

datatable(strain_link_metrics,
          rownames = FALSE,
          class = 'cell-border stripe')
```
Gilliamella and Snodgrassella edges are only in cluster 1 (or otherwise there are only 2 matching edges in the cluster), where only a minority of edges correspond to known strain-linked gene associations.


# Functional enrichments in cluster 1 {.tabset}

**PTS was the only function at all which was significant. This KEGG pathway was significantly negatively enriched in cluster 1 (0.745 odds ratio).**

```{r cluster1_nodes}
cluster1_nodes <- names(net_components$membership[which(net_components$membership == 1)])

cluster1_nodes_by_phylotype <- list()

for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
  cluster1_nodes_by_phylotype[[phylotype]] <- grep(phylotype, cluster1_nodes, value = TRUE)
}

background_sets <- list()
for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
  background_sets[[phylotype]] <- grep(phylotype, tested_genes, value = TRUE)
}

```

## KOs

```{r identify_enriched_KOs_cluster1}
hist(test_for_enriched_gene_families(gene_set = panaroo2KO[cluster1_nodes, "V2"],
                                  background_set = panaroo2KO[tested_genes, "V2"],
                                  min_count_in_background = 3)$fisher_BH)
```

## KEGG pathways


```{r identify_enriched_KEGG_pathways_cluster1}

  gene_set_KOs <- panaroo2KO[cluster1_nodes, "V2"]
  background_set_KOs <- panaroo2KO[tested_genes, "V2"]

  pathway_set_in <- c()
  background_set_in <- c()
  
  for(pathway in names(pathway2KO)) {
    pathway_set_in <- c(pathway_set_in, rep(pathway, times = length(which(gene_set_KOs %in% pathway2KO[[pathway]]))))
    background_set_in <- c(background_set_in, rep(pathway, times = length(which(background_set_KOs %in% pathway2KO[[pathway]]))))
  }

hist(test_for_enriched_gene_families(gene_set = pathway_set_in,
                                  background_set = background_set_in,
                                  min_count_in_background = 3)$fisher_BH)
```

## KEGG modules

```{r identify_enriched_KEGG_modules_cluster1}

  gene_set_KOs <- panaroo2KO[cluster1_nodes, "V2"]
  background_set_KOs <- panaroo2KO[tested_genes, "V2"]

  module_set_in <- c()
  background_set_in <- c()
  
  for(module in names(module2KO)) {
    module_set_in <- c(module_set_in, rep(module, times = length(which(gene_set_KOs %in% module2KO[[module]]))))
    background_set_in <- c(background_set_in, rep(module, times = length(which(background_set_KOs %in% module2KO[[module]]))))
  }

hist(test_for_enriched_gene_families(gene_set = module_set_in,
                                  background_set = background_set_in,
                                  min_count_in_background = 3)$fisher_BH)
```

## CAZy gene families

```{r identify_enriched_CAZy_genefamily_cluster1}

hist(test_for_enriched_gene_families(gene_set = panaroo2CAZy[cluster1_nodes, "V2"],
                                  background_set = panaroo2CAZy[tested_genes, "V2"],
                                  min_count_in_background = 3)$fisher_BH)

```

## CAZy categories

```{r identify_enriched_CAZy_categories_cluster1}

gene_set_in <- gsub("\\d*", "", panaroo2CAZy[cluster1_nodes, "V2"])
gene_set_in <- gsub("_", "", gene_set_in)

background_set_in <- gsub("\\d*", "", panaroo2CAZy[tested_genes, "V2"])
background_set_in <- gsub("_", "", background_set_in)

hist(test_for_enriched_gene_families(gene_set = gene_set_in,
                                  background_set = background_set_in,
                                  min_count_in_background = 3)$fisher_BH)

```


# Identifying sub-modules of cluster 1

```{r get_sub_modules_fast}
cluster_fast_greedy_out <- cluster_fast_greedy(graph = net, )
```


```{r plot_sub_module_painted_network}
net_flattened_subsetted_cluster1 <- net_flattened_subsetted[which(net_flattened_subsetted$membership == "1"), ] 

net_flattened_subsetted_cluster1$submodule <- membership(cluster_fast_greedy_out)[net_flattened_subsetted_cluster1$name]

net_flattened_subsetted_cluster1$submodule_factor <- factor(net_flattened_subsetted_cluster1$submodule)

diverse_col_14 <- c("#b3398f",
                    "#77bb3c",
                    "#9a57ca",
                    "#61c073",
                    "#e26fcf",
                    "#4c8832",
                    "#5e6ccc",
                    "#d79c30",
                    "#5e93cd",
                    "#c6572d",
                    "#4bc2b6",
                    "#d6414c",
                    "#3c8861",
                    "#dd4a84")

ggplot(net_flattened_subsetted_cluster1, aes(x = x, y = y, xend = xend, yend = yend)) +
        geom_edges() +
        geom_nodes(aes(color = submodule_factor), size = 3) +
        scale_color_manual(values = diverse_col_14) +
        theme_blank()

separate_submodules <- names(table(net_flattened_subsetted_cluster1$submodule))
```



# Strain-linkedness of each sub-module in cluster 1

```{r strain_linkedness_table_submodules}

patterns_to_search <- list()
patterns_to_search[["Firm5"]] <- "Firm5.*Firm5"
patterns_to_search[["Gilliamella"]] <- "Gilliamella.*Gilliamella"
patterns_to_search[["Snodgrassella"]] <- "Snodgrassella.*Snodgrassella"

strain_link_metrics_cluster1 <- data.frame(matrix(NA, nrow = length(cluster2keep), ncol = 7))
colnames(strain_link_metrics_cluster1) <- c("submodule", "Firm5_count", "Firm5_percent",
                                   "Gilliamella_count", "Gilliamella_percent", "Snodgrassella_count", "Snodgrassella_percent")

row_i <- 1

for (submodule in separate_submodules) {

  strain_link_metrics_cluster1[row_i, "submodule"] <- submodule
  
  cluster_edges <- get_edges_between_node_set(nodes=unique(net_flattened_subsetted_cluster1[which(net_flattened_subsetted_cluster1$submodule == submodule), "name"]),
                                              edges=discover_output)

  for (phylotype in names(patterns_to_search)) {
    
    if (length(grep(patterns_to_search[[phylotype]], cluster_edges)) >= 0) {
    
      strain_link_metrics_cluster1[row_i, grep(phylotype, colnames(strain_link_metrics_cluster1))] <- determine_percent_phylotype_linked_edges(edge_set=cluster_edges,
                                                                                                                             phylotype_pattern = patterns_to_search[[phylotype]],
                                                                                                                             strain_linked_hits=spydrpick_hits[[phylotype]])
    }  
    
  }
  
  row_i <- row_i + 1
  
}

datatable(strain_link_metrics_cluster1,
          rownames = FALSE,
          class = 'cell-border stripe')
```



# Functional enrichments in sub-modules of cluster 1 {.tabset}

## KOs

```{r identify_enriched_KOs_cluster1_submodules}
fisher_out_df <- data.frame(matrix(NA, nrow = 0, ncol = 6))
colnames(fisher_out_df) <- c("submodule", "phylotype", "func", "func_descrip", "OR", "BH")
  
for (submodule in separate_submodules) {
  
  submodule_nodes <- unique(net_flattened_subsetted_cluster1[which(net_flattened_subsetted_cluster1$submodule == submodule), "name"])

  for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
    
    phylotype_submodule_nodes <- grep(phylotype, submodule_nodes, value = TRUE)
    
    if (length(phylotype_submodule_nodes) < 5) { next }
    
    KO_phylotype_out <- test_for_enriched_gene_families(gene_set = panaroo2KO[phylotype_submodule_nodes, "V2"],
                                                         background_set = panaroo2KO[background_sets[[phylotype]], "V2"],
                                                         min_count_in_background = 5)
  
    if (length(which(KO_phylotype_out$fisher_BH < 0.3)) > 0) {
     sig_func <- names(which(KO_phylotype_out$fisher_BH < 0.3))
     
     fisher_out_df <- rbind(fisher_out_df,
                            data.frame(submodule = submodule,
                                       phylotype = phylotype,
                                       func = sig_func,
                                       func_descrip = KO_descrip[sig_func, 1],
                                       OR = KO_phylotype_out$fisher_or[sig_func],
                                       BH = KO_phylotype_out$fisher_BH[sig_func]))
     
   }
  
  }
  
}

datatable(fisher_out_df,
          rownames = FALSE,
          class = 'cell-border stripe')

```



## KEGG pathways

```{r identify_enriched_KEGG_pathways_cluster1_submodules}

  fisher_out_df <- data.frame(matrix(NA, nrow = 0, ncol = 6))
  colnames(fisher_out_df) <- c("submodule", "phylotype", "func", "func_descrip", "OR", "BH")
    
  for (submodule in separate_submodules) {
    
    submodule_nodes <- unique(net_flattened_subsetted_cluster1[which(net_flattened_subsetted_cluster1$submodule == submodule), "name"])
    
    for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
      
      phylotype_submodule_nodes <- grep(phylotype, submodule_nodes, value = TRUE)
      
      if (length(phylotype_submodule_nodes) < 5) { next }
      
      gene_set_KOs <- panaroo2KO[phylotype_submodule_nodes, "V2"]
      background_set_KOs <- panaroo2KO[grep(phylotype, rownames(panaroo2KO)), "V2"]
      
      pathway_set_in <- c()
      background_set_in <- c()
  
      for(pathway in names(pathway2KO)) {
        pathway_set_in <- c(pathway_set_in, rep(pathway, times = length(which(gene_set_KOs %in% pathway2KO[[pathway]]))))
        background_set_in <- c(background_set_in, rep(pathway, times = length(which(background_set_KOs %in% pathway2KO[[pathway]]))))
      }
      
      if (length(pathway_set_in) < 5) { next }

      pathway_phylotype_out <- test_for_enriched_gene_families(gene_set = pathway_set_in,
                                                           background_set = background_set_in,
                                                           min_count_in_background = 5)
    
      if (length(which(pathway_phylotype_out$fisher_BH < 0.3)) > 0) {
       sig_func <- names(which(pathway_phylotype_out$fisher_BH < 0.3))
       
       fisher_out_df <- rbind(fisher_out_df,
                              data.frame(submodule = submodule,
                                         phylotype = phylotype,
                                         func = sig_func,
                                         func_descrip = pathway_descrip[sig_func, 1],
                                         OR = pathway_phylotype_out$fisher_or[sig_func],
                                         BH = pathway_phylotype_out$fisher_BH[sig_func]))
       
     }
    
    }
    
  }
  
  datatable(fisher_out_df,
            rownames = FALSE,
            class = 'cell-border stripe')
```

## KEGG modules

```{r identify_enriched_KEGG_modules_cluster1_submodules}

  fisher_out_df <- data.frame(matrix(NA, nrow = 0, ncol = 6))
  colnames(fisher_out_df) <- c("submodule", "phylotype", "func", "func_descrip", "OR", "BH")
    
  for (submodule in separate_submodules) {
    
    submodule_nodes <- unique(net_flattened_subsetted_cluster1[which(net_flattened_subsetted_cluster1$submodule == submodule), "name"])
    
    for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
      
      phylotype_submodule_nodes <- grep(phylotype, submodule_nodes, value = TRUE)
      
      if (length(phylotype_submodule_nodes) < 5) { next }
      
      gene_set_KOs <- panaroo2KO[phylotype_submodule_nodes, "V2"]
      background_set_KOs <- panaroo2KO[grep(phylotype, rownames(panaroo2KO)), "V2"]
      
      module_set_in <- c()
      background_set_in <- c()
  
      for(module in names(module2KO)) {
        module_set_in <- c(module_set_in, rep(module, times = length(which(gene_set_KOs %in% module2KO[[module]]))))
        background_set_in <- c(background_set_in, rep(module, times = length(which(background_set_KOs %in% module2KO[[module]]))))
      }
      
      if (length(module_set_in) < 5) { next }

      module_phylotype_out <- test_for_enriched_gene_families(gene_set = module_set_in,
                                                           background_set = background_set_in,
                                                           min_count_in_background = 5)
    
      if (length(which(module_phylotype_out$fisher_BH < 0.3)) > 0) {
       sig_func <- names(which(module_phylotype_out$fisher_BH < 0.3))
       
       fisher_out_df <- rbind(fisher_out_df,
                              data.frame(submodule = submodule,
                                         phylotype = phylotype,
                                         func = sig_func,
                                         func_descrip = module_descrip[sig_func, 1],
                                         OR = module_phylotype_out$fisher_or[sig_func],
                                         BH = module_phylotype_out$fisher_BH[sig_func]))
       
     }
    
    }
    
  }
  
  datatable(fisher_out_df,
            rownames = FALSE,
            class = 'cell-border stripe')
```

## CAZy gene families

```{r identify_enriched_CAZy_genefamily_cluster1_submodules}
fisher_out_df <- data.frame(matrix(NA, nrow = 0, ncol = 6))
colnames(fisher_out_df) <- c("submodule", "phylotype", "func", "func_descrip", "OR", "BH")
  
for (submodule in separate_submodules) {
  
  submodule_nodes <- unique(net_flattened_subsetted_cluster1[which(net_flattened_subsetted_cluster1$submodule == submodule), "name"])

  for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
    
    phylotype_submodule_nodes <- grep(phylotype, submodule_nodes, value = TRUE)
    
    if (length(which(! is.na(panaroo2CAZy[phylotype_submodule_nodes, "V2"]))) < 5) { next }
    
    CAZy_phylotype_out <- test_for_enriched_gene_families(gene_set = panaroo2CAZy[phylotype_submodule_nodes, "V2"],
                                                         background_set = panaroo2CAZy[background_sets[[phylotype]], "V2"],
                                                         min_count_in_background = 5)
  
    if (("fisher_BH" %in% names(CAZy_phylotype_out)) && (length(which(CAZy_phylotype_out$fisher_BH < 0.3)) > 0)) {
     sig_func <- names(which(CAZy_phylotype_out$fisher_BH < 0.3))
     
     fisher_out_df <- rbind(fisher_out_df,
                            data.frame(submodule = submodule,
                                       phylotype = phylotype,
                                       func = sig_func,
                                       func_descrip = CAZy_descrip[sig_func, 1],
                                       OR = CAZy_phylotype_out$fisher_or[sig_func],
                                       BH = CAZy_phylotype_out$fisher_BH[sig_func]))
     
   }
  }
}

datatable(fisher_out_df,
          rownames = FALSE,
          class = 'cell-border stripe')
```

## CAZy categories

```{r identify_enriched_CAZy_categories_cluster1_submodules}
fisher_out_df <- data.frame(matrix(NA, nrow = 0, ncol = 6))
colnames(fisher_out_df) <- c("submodule", "phylotype", "func", "func_descrip", "OR", "BH")
  
for (submodule in separate_submodules) {
  
  submodule_nodes <- unique(net_flattened_subsetted_cluster1[which(net_flattened_subsetted_cluster1$submodule == submodule), "name"])

  for (phylotype in c("Bifidobacterium", "Firm4", "Firm5", "Gilliamella", "Snodgrassella")) {
    
    phylotype_submodule_nodes <- grep(phylotype, submodule_nodes, value = TRUE)
    
    if (length(which(! is.na(panaroo2CAZy[phylotype_submodule_nodes, "V2"]))) < 5) { next }
    
    gene_set_in <- gsub("\\d*", "", panaroo2CAZy[phylotype_submodule_nodes, "V2"])
    gene_set_in <- gsub("_", "", gene_set_in)
    
    background_set_in <- gsub("\\d*", "", panaroo2CAZy[background_sets[[phylotype]], "V2"])
    background_set_in <- gsub("_", "", background_set_in)
        
    CAZy_phylotype_out <- test_for_enriched_gene_families(gene_set = gene_set_in,
                                                         background_set = background_set_in,
                                                         min_count_in_background = 5)
  
    if (("fisher_BH" %in% names(CAZy_phylotype_out)) && (length(which(CAZy_phylotype_out$fisher_BH < 0.3)) > 0)) {
     sig_func <- names(which(CAZy_phylotype_out$fisher_BH < 0.3))
     
     fisher_out_df <- rbind(fisher_out_df,
                            data.frame(submodule = submodule,
                                       phylotype = phylotype,
                                       func = sig_func,
                                       func_descrip = CAZy_descrip[sig_func, 1],
                                       OR = CAZy_phylotype_out$fisher_or[sig_func],
                                       BH = CAZy_phylotype_out$fisher_BH[sig_func]))
     
   }
  }
}

datatable(fisher_out_df,
          rownames = FALSE,
          class = 'cell-border stripe')
```



# Session info {.tabset}

## Hide

## Show

```{r session_info}
sessionInfo()
```
