---
title: "PCA based on pandora presence / absence"
author: "Gavin Douglas"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
library(cowplot)
library(DT)
library(ggbeeswarm)
library(ggplot2)
library(kableExtra)
library(knitr)
```

# Read in data

```{r read_in_pandora}
pandora_output <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/pandora_running/pandora_multisample.matrix",
                             header = TRUE, sep = "\t", row.names = 1)
rownames(pandora_output) <- gsub("\\.fa$", "", rownames(pandora_output))

# Dataset samples
Ellegaard.2019_samples <- read.table("/home/gdouglas/projects/honey_bee/Ellegaard/SRR_ids.txt", stringsAsFactors = FALSE)$V1
Ellegaard.2020_samples <- read.table("/data1/gdouglas/projects/honey_bee/Ellegaard.2020/PRJNA598094_SRR_ids.txt", stringsAsFactors = FALSE)$V1

pandora_output <- pandora_output[, c(Ellegaard.2019_samples, Ellegaard.2020_samples)]

pandora_output <- pandora_output[-which(rowSums(pandora_output) == ncol(pandora_output)), ]
```

```{r read_sample_info}
sample_names_2019 <- read.table("/home/gdouglas/projects/honey_bee/Ellegaard/PRJNA473901_SRR_to_sample.txt",
                                header = FALSE, sep = "\t", stringsAsFactors = FALSE)
colnames(sample_names_2019) <- c("SRR", "sample")

sample_names_2019$colony <- gsub("Y.*$", "", sample_names_2019$sample)

sample_names_2019$location <- gsub("_.*$", "", sample_names_2019$sample)
sample_names_2019$location <- gsub("^.*Y", "", sample_names_2019$location)

sample_names_2019$age_raw <- gsub(".*_", "", sample_names_2019$sample)
sample_names_2019$age <- NA
sample_names_2019[grep("W", sample_names_2019$age_raw), "age"] <- "Old"
sample_names_2019[grep("F", sample_names_2019$age_raw), "age"] <- "Middle-aged"
sample_names_2019[grep("N", sample_names_2019$age_raw), "age"] <- "Young"


sample_names_2020 <- read.table("/data1/gdouglas/projects/honey_bee/Ellegaard.2020/PRJNA598094_SRR_to_sample.txt",
                                header = FALSE, sep = "\t", stringsAsFactors = FALSE)
colnames(sample_names_2020) <- c("SRR", "sample")

sample_names_2020$apiary <- NA
sample_names_2020$apiary[grep("Ai", sample_names_2020$sample)] <- "Ai"
sample_names_2020$apiary[grep("Iu", sample_names_2020$sample)] <- "Iu"
```

# Identify major outliers based on number of genes {.tabset}

## Hist
```{r num_genes}
hist(colSums(pandora_output), breaks = 50, xlab = "Number of genes", ylab = "Number of samples", main = "", xlim = c(0, 10000))
```

## Num genes vs depth of FASTQs input to pandora

```{r old_depth_vs_pandora_num_genes}

total_reads <- c()

for (SRR in c(Ellegaard.2019_samples, Ellegaard.2020_samples)) {
  wc_file <- paste("/data1/gdouglas/projects/honey_bee/filtered_fastqs/Ellegaard.2019.2020_cat_wc_output/", SRR, ".fastq.gz.wc.txt", sep = "")
  total_reads <- c(total_reads, as.numeric(readLines(wc_file)))
}

plot(total_reads, colSums(pandora_output), xlab = "Number of input reads to pandora", ylab = "Number of genes called as present")

```

# PCAs {.tabset}

```{r filter_out_major_outliers}
pandora_output <- pandora_output[, -which(colSums(pandora_output) < 2000)]

if (length(which(rowSums(pandora_output) == 0)) > 0) {
 pandora_output <- pandora_output[-which(rowSums(pandora_output) == 0), ]
}

if (length(which(! Ellegaard.2019_samples %in% colnames(pandora_output))) > 0) {
  Ellegaard.2019_samples <- Ellegaard.2019_samples[-which(! Ellegaard.2019_samples %in% colnames(pandora_output))]
  sample_names_2019 <- sample_names_2019[-which(! sample_names_2019$SRR %in% colnames(pandora_output)), ]
}

if (length(which(! Ellegaard.2020_samples %in% colnames(pandora_output))) > 0) {
  Ellegaard.2020_samples <- Ellegaard.2020_samples[-which(! Ellegaard.2020_samples %in% colnames(pandora_output))]
  sample_names_2020 <- sample_names_2020[-which(! sample_names_2020$SRR %in% colnames(pandora_output)), ]
}
```

## All genes (any phylotype) {.tabset}

```{r ALL_prep}
ALL_pandora_output <- dist(t(pandora_output), method = "binary")
ALL_pandora_PCA <- prcomp(ALL_pandora_output, scale. = TRUE, center = TRUE)
ALL_pandora_PCA_df <- data.frame(ALL_pandora_PCA$x)
ALL_pandora_PCA_imp <- data.frame(summary(ALL_pandora_PCA)$importance)
ALL_pandora_PCA_percent <- data.frame(t(ALL_pandora_PCA_imp["Proportion of Variance", ])) * 100
ALL_pandora_PCA_percent$Proportion.of.Variance <- round(ALL_pandora_PCA_percent$Proportion.of.Variance, digits = 1)
ALL_pandora_PCA_percent$Proportion.of.Variance <- as.character(ALL_pandora_PCA_percent$Proportion.of.Variance)

# Country of origin (i.e., which paper it was from)
ALL_pandora_PCA_df$Country <- NA
ALL_pandora_PCA_df[Ellegaard.2019_samples, "Country"] <- "Switzerland"
ALL_pandora_PCA_df[Ellegaard.2020_samples, "Country"] <- "Japan"


ALL_pandora_PCA_df$Year <- NA
ALL_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "1"), "SRR"], "Year"] <- "2019_1"
ALL_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "2"), "SRR"], "Year"] <- "2019_2"
ALL_pandora_PCA_df[Ellegaard.2020_samples, "Year"] <- "2020"


ALL_pandora_PCA_df$Location <- NA
ALL_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Dr"), "SRR"], "Location"] <- "Les Droites"
ALL_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Gr"), "SRR"], "Location"] <- "Grammont"
ALL_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Ai"), "SRR"], "Location"] <- "Ai"
ALL_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Iu"), "SRR"], "Location"] <- "Iu"

ALL_pandora_PCA_df$Age <- NA
ALL_pandora_PCA_df[sample_names_2019$SRR, "Age"] <- sample_names_2019$age
ALL_pandora_PCA_df[Ellegaard.2020_samples, "Age"] <- "Young"

ALL_pandora_PCA_df$Age <- factor(ALL_pandora_PCA_df$Age, levels = c("Young", "Middle-aged", "Old"))

```

### Age and country

```{r ALL_age_and_country, fig.width=20, fig.height = 6}
ALL_PC1_vs_PC2_age_and_country <- ggplot(data = ALL_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", ALL_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", ALL_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

ALL_PC1_vs_PC3_age_and_country <- ggplot(data = ALL_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", ALL_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", ALL_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(ALL_PC1_vs_PC2_age_and_country, ALL_PC1_vs_PC3_age_and_country, nrow = 1, ncol = 2)

```

### Age and Location

```{r ALL_age_and_Location, fig.width=20, fig.height = 6}
ALL_PC1_vs_PC2_age_and_Location <- ggplot(data = ALL_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", ALL_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", ALL_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

ALL_PC1_vs_PC3_age_and_Location <- ggplot(data = ALL_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", ALL_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", ALL_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(ALL_PC1_vs_PC2_age_and_Location, ALL_PC1_vs_PC3_age_and_Location, nrow = 1, ncol = 2)
```

### Age and Year

```{r ALL_age_and_Year, fig.width=20, fig.height = 6}
ALL_PC1_vs_PC2_age_and_Year <- ggplot(data = ALL_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", ALL_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", ALL_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

ALL_PC1_vs_PC3_age_and_Year <- ggplot(data = ALL_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", ALL_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", ALL_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(ALL_PC1_vs_PC2_age_and_Year, ALL_PC1_vs_PC3_age_and_Year, nrow = 1, ncol = 2)
```

## Bifidobacterium {.tabset}

```{r Bifidobacterium_prep}
Bifidobacterium_pandora_output <- dist(t(pandora_output[grep("Bifidobacterium", rownames(pandora_output)), ]), method = "binary")
Bifidobacterium_pandora_PCA <- prcomp(Bifidobacterium_pandora_output, scale. = TRUE, center = TRUE)
Bifidobacterium_pandora_PCA_df <- data.frame(Bifidobacterium_pandora_PCA$x)
Bifidobacterium_pandora_PCA_imp <- data.frame(summary(Bifidobacterium_pandora_PCA)$importance)
Bifidobacterium_pandora_PCA_percent <- data.frame(t(Bifidobacterium_pandora_PCA_imp["Proportion of Variance", ])) * 100
Bifidobacterium_pandora_PCA_percent$Proportion.of.Variance <- round(Bifidobacterium_pandora_PCA_percent$Proportion.of.Variance, digits = 1)
Bifidobacterium_pandora_PCA_percent$Proportion.of.Variance <- as.character(Bifidobacterium_pandora_PCA_percent$Proportion.of.Variance)

# Country of origin (i.e., which paper it was from)
Bifidobacterium_pandora_PCA_df$Country <- NA
Bifidobacterium_pandora_PCA_df[Ellegaard.2019_samples, "Country"] <- "Switzerland"
Bifidobacterium_pandora_PCA_df[Ellegaard.2020_samples, "Country"] <- "Japan"


Bifidobacterium_pandora_PCA_df$Year <- NA
Bifidobacterium_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "1"), "SRR"], "Year"] <- "2019_1"
Bifidobacterium_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "2"), "SRR"], "Year"] <- "2019_2"
Bifidobacterium_pandora_PCA_df[Ellegaard.2020_samples, "Year"] <- "2020"


Bifidobacterium_pandora_PCA_df$Location <- NA
Bifidobacterium_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Dr"), "SRR"], "Location"] <- "Les Droites"
Bifidobacterium_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Gr"), "SRR"], "Location"] <- "Grammont"
Bifidobacterium_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Ai"), "SRR"], "Location"] <- "Ai"
Bifidobacterium_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Iu"), "SRR"], "Location"] <- "Iu"

Bifidobacterium_pandora_PCA_df$Age <- NA
Bifidobacterium_pandora_PCA_df[sample_names_2019$SRR, "Age"] <- sample_names_2019$age
Bifidobacterium_pandora_PCA_df[Ellegaard.2020_samples, "Age"] <- "Young"

Bifidobacterium_pandora_PCA_df$Age <- factor(Bifidobacterium_pandora_PCA_df$Age, levels = c("Young", "Middle-aged", "Old"))

```

### Age and country

```{r Bifidobacterium_age_and_country, fig.width=20, fig.height = 6}
Bifidobacterium_PC1_vs_PC2_age_and_country <- ggplot(data = Bifidobacterium_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Bifidobacterium_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Bifidobacterium_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Bifidobacterium_PC1_vs_PC3_age_and_country <- ggplot(data = Bifidobacterium_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Bifidobacterium_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Bifidobacterium_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Bifidobacterium_PC1_vs_PC2_age_and_country, Bifidobacterium_PC1_vs_PC3_age_and_country, nrow = 1, ncol = 2)

```

### Age and Location

```{r Bifidobacterium_age_and_Location, fig.width=20, fig.height = 6}
Bifidobacterium_PC1_vs_PC2_age_and_Location <- ggplot(data = Bifidobacterium_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Bifidobacterium_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Bifidobacterium_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Bifidobacterium_PC1_vs_PC3_age_and_Location <- ggplot(data = Bifidobacterium_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Bifidobacterium_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Bifidobacterium_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Bifidobacterium_PC1_vs_PC2_age_and_Location, Bifidobacterium_PC1_vs_PC3_age_and_Location, nrow = 1, ncol = 2)
```

### Age and Year

```{r Bifidobacterium_age_and_Year, fig.width=20, fig.height = 6}
Bifidobacterium_PC1_vs_PC2_age_and_Year <- ggplot(data = Bifidobacterium_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Bifidobacterium_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Bifidobacterium_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Bifidobacterium_PC1_vs_PC3_age_and_Year <- ggplot(data = Bifidobacterium_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Bifidobacterium_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Bifidobacterium_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Bifidobacterium_PC1_vs_PC2_age_and_Year, Bifidobacterium_PC1_vs_PC3_age_and_Year, nrow = 1, ncol = 2)
```


## Firm4 {.tabset}

```{r Firm4_prep}
Firm4_pandora_output <- dist(t(pandora_output[grep("Firm4", rownames(pandora_output)), ]), method = "binary")
Firm4_pandora_PCA <- prcomp(Firm4_pandora_output, scale. = TRUE, center = TRUE)
Firm4_pandora_PCA_df <- data.frame(Firm4_pandora_PCA$x)
Firm4_pandora_PCA_imp <- data.frame(summary(Firm4_pandora_PCA)$importance)
Firm4_pandora_PCA_percent <- data.frame(t(Firm4_pandora_PCA_imp["Proportion of Variance", ])) * 100
Firm4_pandora_PCA_percent$Proportion.of.Variance <- round(Firm4_pandora_PCA_percent$Proportion.of.Variance, digits = 1)
Firm4_pandora_PCA_percent$Proportion.of.Variance <- as.character(Firm4_pandora_PCA_percent$Proportion.of.Variance)

# Country of origin (i.e., which paper it was from)
Firm4_pandora_PCA_df$Country <- NA
Firm4_pandora_PCA_df[Ellegaard.2019_samples, "Country"] <- "Switzerland"
Firm4_pandora_PCA_df[Ellegaard.2020_samples, "Country"] <- "Japan"


Firm4_pandora_PCA_df$Year <- NA
Firm4_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "1"), "SRR"], "Year"] <- "2019_1"
Firm4_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "2"), "SRR"], "Year"] <- "2019_2"
Firm4_pandora_PCA_df[Ellegaard.2020_samples, "Year"] <- "2020"


Firm4_pandora_PCA_df$Location <- NA
Firm4_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Dr"), "SRR"], "Location"] <- "Les Droites"
Firm4_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Gr"), "SRR"], "Location"] <- "Grammont"
Firm4_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Ai"), "SRR"], "Location"] <- "Ai"
Firm4_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Iu"), "SRR"], "Location"] <- "Iu"

Firm4_pandora_PCA_df$Age <- NA
Firm4_pandora_PCA_df[sample_names_2019$SRR, "Age"] <- sample_names_2019$age
Firm4_pandora_PCA_df[Ellegaard.2020_samples, "Age"] <- "Young"

Firm4_pandora_PCA_df$Age <- factor(Firm4_pandora_PCA_df$Age, levels = c("Young", "Middle-aged", "Old"))

```

### Age and country

```{r Firm4_age_and_country, fig.width=20, fig.height = 6}
Firm4_PC1_vs_PC2_age_and_country <- ggplot(data = Firm4_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm4_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Firm4_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Firm4_PC1_vs_PC3_age_and_country <- ggplot(data = Firm4_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm4_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Firm4_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Firm4_PC1_vs_PC2_age_and_country, Firm4_PC1_vs_PC3_age_and_country, nrow = 1, ncol = 2)

```

### Age and Location

```{r Firm4_age_and_Location, fig.width=20, fig.height = 6}
Firm4_PC1_vs_PC2_age_and_Location <- ggplot(data = Firm4_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm4_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Firm4_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Firm4_PC1_vs_PC3_age_and_Location <- ggplot(data = Firm4_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm4_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Firm4_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Firm4_PC1_vs_PC2_age_and_Location, Firm4_PC1_vs_PC3_age_and_Location, nrow = 1, ncol = 2)
```

### Age and Year

```{r Firm4_age_and_Year, fig.width=20, fig.height = 6}
Firm4_PC1_vs_PC2_age_and_Year <- ggplot(data = Firm4_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm4_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Firm4_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Firm4_PC1_vs_PC3_age_and_Year <- ggplot(data = Firm4_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm4_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Firm4_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Firm4_PC1_vs_PC2_age_and_Year, Firm4_PC1_vs_PC3_age_and_Year, nrow = 1, ncol = 2)
```




## Firm5 {.tabset}

```{r Firm5_prep}
Firm5_pandora_output <- dist(t(pandora_output[grep("Firm5", rownames(pandora_output)), ]), method = "binary")
Firm5_pandora_PCA <- prcomp(Firm5_pandora_output, scale. = TRUE, center = TRUE)
Firm5_pandora_PCA_df <- data.frame(Firm5_pandora_PCA$x)
Firm5_pandora_PCA_imp <- data.frame(summary(Firm5_pandora_PCA)$importance)
Firm5_pandora_PCA_percent <- data.frame(t(Firm5_pandora_PCA_imp["Proportion of Variance", ])) * 100
Firm5_pandora_PCA_percent$Proportion.of.Variance <- round(Firm5_pandora_PCA_percent$Proportion.of.Variance, digits = 1)
Firm5_pandora_PCA_percent$Proportion.of.Variance <- as.character(Firm5_pandora_PCA_percent$Proportion.of.Variance)

# Country of origin (i.e., which paper it was from)
Firm5_pandora_PCA_df$Country <- NA
Firm5_pandora_PCA_df[Ellegaard.2019_samples, "Country"] <- "Switzerland"
Firm5_pandora_PCA_df[Ellegaard.2020_samples, "Country"] <- "Japan"


Firm5_pandora_PCA_df$Year <- NA
Firm5_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "1"), "SRR"], "Year"] <- "2019_1"
Firm5_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "2"), "SRR"], "Year"] <- "2019_2"
Firm5_pandora_PCA_df[Ellegaard.2020_samples, "Year"] <- "2020"


Firm5_pandora_PCA_df$Location <- NA
Firm5_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Dr"), "SRR"], "Location"] <- "Les Droites"
Firm5_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Gr"), "SRR"], "Location"] <- "Grammont"
Firm5_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Ai"), "SRR"], "Location"] <- "Ai"
Firm5_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Iu"), "SRR"], "Location"] <- "Iu"

Firm5_pandora_PCA_df$Age <- NA
Firm5_pandora_PCA_df[sample_names_2019$SRR, "Age"] <- sample_names_2019$age
Firm5_pandora_PCA_df[Ellegaard.2020_samples, "Age"] <- "Young"

Firm5_pandora_PCA_df$Age <- factor(Firm5_pandora_PCA_df$Age, levels = c("Young", "Middle-aged", "Old"))

```

### Age and country

```{r Firm5_age_and_country, fig.width=20, fig.height = 6}
Firm5_PC1_vs_PC2_age_and_country <- ggplot(data = Firm5_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm5_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Firm5_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Firm5_PC1_vs_PC3_age_and_country <- ggplot(data = Firm5_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm5_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Firm5_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Firm5_PC1_vs_PC2_age_and_country, Firm5_PC1_vs_PC3_age_and_country, nrow = 1, ncol = 2)

```

### Age and Location

```{r Firm5_age_and_Location, fig.width=20, fig.height = 6}
Firm5_PC1_vs_PC2_age_and_Location <- ggplot(data = Firm5_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm5_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Firm5_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Firm5_PC1_vs_PC3_age_and_Location <- ggplot(data = Firm5_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm5_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Firm5_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Firm5_PC1_vs_PC2_age_and_Location, Firm5_PC1_vs_PC3_age_and_Location, nrow = 1, ncol = 2)
```

### Age and Year

```{r Firm5_age_and_Year, fig.width=20, fig.height = 6}
Firm5_PC1_vs_PC2_age_and_Year <- ggplot(data = Firm5_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm5_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Firm5_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Firm5_PC1_vs_PC3_age_and_Year <- ggplot(data = Firm5_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Firm5_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Firm5_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Firm5_PC1_vs_PC2_age_and_Year, Firm5_PC1_vs_PC3_age_and_Year, nrow = 1, ncol = 2)
```




## Gilliamella {.tabset}

```{r Gilliamella_prep}
Gilliamella_pandora_output <- dist(t(pandora_output[grep("Gilli", rownames(pandora_output)), ]), method = "binary")
Gilliamella_pandora_PCA <- prcomp(Gilliamella_pandora_output, scale. = TRUE, center = TRUE)
Gilliamella_pandora_PCA_df <- data.frame(Gilliamella_pandora_PCA$x)
Gilliamella_pandora_PCA_imp <- data.frame(summary(Gilliamella_pandora_PCA)$importance)
Gilliamella_pandora_PCA_percent <- data.frame(t(Gilliamella_pandora_PCA_imp["Proportion of Variance", ])) * 100
Gilliamella_pandora_PCA_percent$Proportion.of.Variance <- round(Gilliamella_pandora_PCA_percent$Proportion.of.Variance, digits = 1)
Gilliamella_pandora_PCA_percent$Proportion.of.Variance <- as.character(Gilliamella_pandora_PCA_percent$Proportion.of.Variance)

# Country of origin (i.e., which paper it was from)
Gilliamella_pandora_PCA_df$Country <- NA
Gilliamella_pandora_PCA_df[Ellegaard.2019_samples, "Country"] <- "Switzerland"
Gilliamella_pandora_PCA_df[Ellegaard.2020_samples, "Country"] <- "Japan"


Gilliamella_pandora_PCA_df$Year <- NA
Gilliamella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "1"), "SRR"], "Year"] <- "2019_1"
Gilliamella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "2"), "SRR"], "Year"] <- "2019_2"
Gilliamella_pandora_PCA_df[Ellegaard.2020_samples, "Year"] <- "2020"


Gilliamella_pandora_PCA_df$Location <- NA
Gilliamella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Dr"), "SRR"], "Location"] <- "Les Droites"
Gilliamella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Gr"), "SRR"], "Location"] <- "Grammont"
Gilliamella_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Ai"), "SRR"], "Location"] <- "Ai"
Gilliamella_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Iu"), "SRR"], "Location"] <- "Iu"

Gilliamella_pandora_PCA_df$Age <- NA
Gilliamella_pandora_PCA_df[sample_names_2019$SRR, "Age"] <- sample_names_2019$age
Gilliamella_pandora_PCA_df[Ellegaard.2020_samples, "Age"] <- "Young"

Gilliamella_pandora_PCA_df$Age <- factor(Gilliamella_pandora_PCA_df$Age, levels = c("Young", "Middle-aged", "Old"))

```

### Age and country

```{r Gilliamella_age_and_country, fig.width=20, fig.height = 6}
Gilliamella_PC1_vs_PC2_age_and_country <- ggplot(data = Gilliamella_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Gilliamella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Gilliamella_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Gilliamella_PC1_vs_PC3_age_and_country <- ggplot(data = Gilliamella_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Gilliamella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Gilliamella_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Gilliamella_PC1_vs_PC2_age_and_country, Gilliamella_PC1_vs_PC3_age_and_country, nrow = 1, ncol = 2)

```

### Age and Location

```{r Gilliamella_age_and_Location, fig.width=20, fig.height = 6}
Gilliamella_PC1_vs_PC2_age_and_Location <- ggplot(data = Gilliamella_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Gilliamella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Gilliamella_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Gilliamella_PC1_vs_PC3_age_and_Location <- ggplot(data = Gilliamella_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Gilliamella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Gilliamella_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Gilliamella_PC1_vs_PC2_age_and_Location, Gilliamella_PC1_vs_PC3_age_and_Location, nrow = 1, ncol = 2)
```

### Age and Year

```{r Gilliamella_age_and_Year, fig.width=20, fig.height = 6}
Gilliamella_PC1_vs_PC2_age_and_Year <- ggplot(data = Gilliamella_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Gilliamella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Gilliamella_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Gilliamella_PC1_vs_PC3_age_and_Year <- ggplot(data = Gilliamella_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Gilliamella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Gilliamella_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Gilliamella_PC1_vs_PC2_age_and_Year, Gilliamella_PC1_vs_PC3_age_and_Year, nrow = 1, ncol = 2)
```


## Snodgrassella {.tabset}

```{r Snodgrassella_prep}
Snodgrassella_pandora_output <- dist(t(pandora_output[grep("Snod", rownames(pandora_output)), ]), method = "binary")
Snodgrassella_pandora_PCA <- prcomp(Snodgrassella_pandora_output, scale. = TRUE, center = TRUE)
Snodgrassella_pandora_PCA_df <- data.frame(Snodgrassella_pandora_PCA$x)
Snodgrassella_pandora_PCA_imp <- data.frame(summary(Snodgrassella_pandora_PCA)$importance)
Snodgrassella_pandora_PCA_percent <- data.frame(t(Snodgrassella_pandora_PCA_imp["Proportion of Variance", ])) * 100
Snodgrassella_pandora_PCA_percent$Proportion.of.Variance <- round(Snodgrassella_pandora_PCA_percent$Proportion.of.Variance, digits = 1)
Snodgrassella_pandora_PCA_percent$Proportion.of.Variance <- as.character(Snodgrassella_pandora_PCA_percent$Proportion.of.Variance)

# Country of origin (i.e., which paper it was from)
Snodgrassella_pandora_PCA_df$Country <- NA
Snodgrassella_pandora_PCA_df[Ellegaard.2019_samples, "Country"] <- "Switzerland"
Snodgrassella_pandora_PCA_df[Ellegaard.2020_samples, "Country"] <- "Japan"


Snodgrassella_pandora_PCA_df$Year <- NA
Snodgrassella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "1"), "SRR"], "Year"] <- "2019_1"
Snodgrassella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$location == "2"), "SRR"], "Year"] <- "2019_2"
Snodgrassella_pandora_PCA_df[Ellegaard.2020_samples, "Year"] <- "2020"


Snodgrassella_pandora_PCA_df$Location <- NA
Snodgrassella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Dr"), "SRR"], "Location"] <- "Les Droites"
Snodgrassella_pandora_PCA_df[sample_names_2019[which(sample_names_2019$colony == "Gr"), "SRR"], "Location"] <- "Grammont"
Snodgrassella_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Ai"), "SRR"], "Location"] <- "Ai"
Snodgrassella_pandora_PCA_df[sample_names_2020[which(sample_names_2020$apiary == "Iu"), "SRR"], "Location"] <- "Iu"

Snodgrassella_pandora_PCA_df$Age <- NA
Snodgrassella_pandora_PCA_df[sample_names_2019$SRR, "Age"] <- sample_names_2019$age
Snodgrassella_pandora_PCA_df[Ellegaard.2020_samples, "Age"] <- "Young"

Snodgrassella_pandora_PCA_df$Age <- factor(Snodgrassella_pandora_PCA_df$Age, levels = c("Young", "Middle-aged", "Old"))

```

### Age and country

```{r Snodgrassella_age_and_country, fig.width=20, fig.height = 6}
Snodgrassella_PC1_vs_PC2_age_and_country <- ggplot(data = Snodgrassella_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Snodgrassella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Snodgrassella_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Snodgrassella_PC1_vs_PC3_age_and_country <- ggplot(data = Snodgrassella_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Country, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Snodgrassella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Snodgrassella_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Snodgrassella_PC1_vs_PC2_age_and_country, Snodgrassella_PC1_vs_PC3_age_and_country, nrow = 1, ncol = 2)

```

### Age and Location

```{r Snodgrassella_age_and_Location, fig.width=20, fig.height = 6}
Snodgrassella_PC1_vs_PC2_age_and_Location <- ggplot(data = Snodgrassella_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Snodgrassella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Snodgrassella_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Snodgrassella_PC1_vs_PC3_age_and_Location <- ggplot(data = Snodgrassella_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Location, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Snodgrassella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Snodgrassella_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Snodgrassella_PC1_vs_PC2_age_and_Location, Snodgrassella_PC1_vs_PC3_age_and_Location, nrow = 1, ncol = 2)
```

### Age and Year

```{r Snodgrassella_age_and_Year, fig.width=20, fig.height = 6}
Snodgrassella_PC1_vs_PC2_age_and_Year <- ggplot(data = Snodgrassella_pandora_PCA_df, aes(x = PC1, y = PC2, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Snodgrassella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC2 (", Snodgrassella_pandora_PCA_percent["PC2", 1], "%)", sep = ""))

Snodgrassella_PC1_vs_PC3_age_and_Year <- ggplot(data = Snodgrassella_pandora_PCA_df, aes(x = PC1, y = PC3, shape = Year, colour = Age)) +
                                          geom_point(size = 5) +
                                          theme_bw() +
                                          xlab(paste("PC1 (", Snodgrassella_pandora_PCA_percent["PC1", 1], "%)", sep = "")) +
                                          ylab(paste("PC3 (", Snodgrassella_pandora_PCA_percent["PC3", 1], "%)", sep = ""))

plot_grid(Snodgrassella_PC1_vs_PC2_age_and_Year, Snodgrassella_PC1_vs_PC3_age_and_Year, nrow = 1, ncol = 2)
```




# Session info {.tabset}

## Hide

## Show

```{r session_info}
sessionInfo()
```
