---
title: Summarize StrainFinder results each phylotype's core genes. Do this for best-hit, pandora w struct and pandora w/o structs
author: "Gavin Douglas"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(cowplot)
library(ggplot2)
library(ComplexHeatmap)
library(kableExtra)
library(knitr)
```

# Bifidobacterium {.tabset}

## AIC distribution

```{r Bifidobacterium_basic_AICs}

Bifidobacterium_besthit_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/Bifidobacterium_core.strain_fit_summary_more_resources.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Bifidobacterium_besthit_AICs$Datatype <- "besthit"


Bifidobacterium_pandora.nostruct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/Bifidobacterium_core_no.struct.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Bifidobacterium_pandora.nostruct_AICs$Datatype <- "pandora.nostruct"


Bifidobacterium_pandora.struct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct//Bifidobacterium_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Bifidobacterium_pandora.struct_AICs$Datatype <- "pandora.struct"


Bifidobacterium_besthit_AICs_plot <- ggplot(data = Bifidobacterium_besthit_AICs, aes(x = ID, y = AIC)) +
                                            geom_point() +
                                            theme_bw() +
                                            xlab("Number of strains") +
                                            ggtitle("Best-hit")

Bifidobacterium_pandora.nostruct_AICs_plot <- ggplot(data = Bifidobacterium_pandora.nostruct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (no structural)")


Bifidobacterium_pandora.struct_AICs_plot <- ggplot(data = Bifidobacterium_pandora.struct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (with structural)")

plot_grid(Bifidobacterium_besthit_AICs_plot, Bifidobacterium_pandora.nostruct_AICs_plot, Bifidobacterium_pandora.struct_AICs_plot, nrow = 1)
```


## Strain abundances {.tabset}

### Best-hit
```{r Bifidobacterium_besthit_abun}
Bifidobacterium_best_num_strain_best_fit <- as.character(Bifidobacterium_besthit_AICs[which(Bifidobacterium_besthit_AICs$AIC == min(Bifidobacterium_besthit_AICs$AIC)), "ID"])

Bifidobacterium_best_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/otu_table.Bifidobacterium_core.",
                                                              Bifidobacterium_best_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Bifidobacterium_best_num_strain_best_fit_abun <- read.table(file = Bifidobacterium_best_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Bifidobacterium_best_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```


### Pandora (no structural)
```{r Bifidobacterium_pandora_no.struct_abun}
Bifidobacterium_pandora.nostruct_num_strain_best_fit <- as.character(Bifidobacterium_pandora.nostruct_AICs[which(Bifidobacterium_pandora.nostruct_AICs$AIC == min(Bifidobacterium_pandora.nostruct_AICs$AIC)), "ID"])

Bifidobacterium_pandora.nostruct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/otu_table.Bifidobacterium_core_no.struct.",
                                                              Bifidobacterium_pandora.nostruct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Bifidobacterium_pandora.nostruct_num_strain_best_fit_abun <- read.table(file = Bifidobacterium_pandora.nostruct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Bifidobacterium_pandora.nostruct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```

### Pandora (with structural)
```{r Bifidobacterium_pandora_struct_abun}
Bifidobacterium_pandora.struct_num_strain_best_fit <- as.character(Bifidobacterium_pandora.struct_AICs[which(Bifidobacterium_pandora.struct_AICs$AIC == min(Bifidobacterium_pandora.struct_AICs$AIC)), "ID"])

Bifidobacterium_pandora.struct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct/otu_table.Bifidobacterium_core.",
                                                              Bifidobacterium_pandora.struct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Bifidobacterium_pandora.struct_num_strain_best_fit_abun <- read.table(file = Bifidobacterium_pandora.struct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Bifidobacterium_pandora.struct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```



# Firm4 {.tabset}

## AIC distribution

```{r Firm4_basic_AICs}

Firm4_besthit_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/Firm4_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Firm4_besthit_AICs$Datatype <- "besthit"


Firm4_pandora.nostruct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/Firm4_core_no.struct.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Firm4_pandora.nostruct_AICs$Datatype <- "pandora.nostruct"


Firm4_pandora.struct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct//Firm4_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Firm4_pandora.struct_AICs$Datatype <- "pandora.struct"


Firm4_besthit_AICs_plot <- ggplot(data = Firm4_besthit_AICs, aes(x = ID, y = AIC)) +
                                            geom_point() +
                                            theme_bw() +
                                            xlab("Number of strains") +
                                            ggtitle("Best-hit")

Firm4_pandora.nostruct_AICs_plot <- ggplot(data = Firm4_pandora.nostruct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (no structural)")


Firm4_pandora.struct_AICs_plot <- ggplot(data = Firm4_pandora.struct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (with structural)")

plot_grid(Firm4_besthit_AICs_plot, Firm4_pandora.nostruct_AICs_plot, Firm4_pandora.struct_AICs_plot, nrow = 1)
```


## Strain abundances {.tabset}

### Best-hit
```{r Firm4_besthit_abun}
Firm4_best_num_strain_best_fit <- as.character(Firm4_besthit_AICs[which(Firm4_besthit_AICs$AIC == min(Firm4_besthit_AICs$AIC)), "ID"])

Firm4_best_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/otu_table.Firm4_core.",
                                                              Firm4_best_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Firm4_best_num_strain_best_fit_abun <- read.table(file = Firm4_best_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Firm4_best_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```


### Pandora (no structural)
```{r Firm4_pandora_no.struct_abun}
Firm4_pandora.nostruct_num_strain_best_fit <- as.character(Firm4_pandora.nostruct_AICs[which(Firm4_pandora.nostruct_AICs$AIC == min(Firm4_pandora.nostruct_AICs$AIC)), "ID"])

Firm4_pandora.nostruct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/otu_table.Firm4_core_no.struct.",
                                                              Firm4_pandora.nostruct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Firm4_pandora.nostruct_num_strain_best_fit_abun <- read.table(file = Firm4_pandora.nostruct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Firm4_pandora.nostruct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```

### Pandora (with structural)
```{r Firm4_pandora_struct_abun}
Firm4_pandora.struct_num_strain_best_fit <- as.character(Firm4_pandora.struct_AICs[which(Firm4_pandora.struct_AICs$AIC == min(Firm4_pandora.struct_AICs$AIC)), "ID"])

Firm4_pandora.struct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct/otu_table.Firm4_core.",
                                                              Firm4_pandora.struct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Firm4_pandora.struct_num_strain_best_fit_abun <- read.table(file = Firm4_pandora.struct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Firm4_pandora.struct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```




# Firm5 {.tabset}

## AIC distribution

```{r Firm5_basic_AICs}

Firm5_besthit_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/Firm5_core.strain_fit_summary_more_resources.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Firm5_besthit_AICs$Datatype <- "besthit"


Firm5_pandora.nostruct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/Firm5_core_no.struct.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Firm5_pandora.nostruct_AICs$Datatype <- "pandora.nostruct"


Firm5_pandora.struct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct//Firm5_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Firm5_pandora.struct_AICs$Datatype <- "pandora.struct"


Firm5_besthit_AICs_plot <- ggplot(data = Firm5_besthit_AICs, aes(x = ID, y = AIC)) +
                                            geom_point() +
                                            theme_bw() +
                                            xlab("Number of strains") +
                                            ggtitle("Best-hit")

Firm5_pandora.nostruct_AICs_plot <- ggplot(data = Firm5_pandora.nostruct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (no structural)")


Firm5_pandora.struct_AICs_plot <- ggplot(data = Firm5_pandora.struct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (with structural)")

plot_grid(Firm5_besthit_AICs_plot, Firm5_pandora.nostruct_AICs_plot, Firm5_pandora.struct_AICs_plot, nrow = 1)
```


## Strain abundances {.tabset}

### Best-hit
```{r Firm5_besthit_abun}
Firm5_best_num_strain_best_fit <- as.character(Firm5_besthit_AICs[which(Firm5_besthit_AICs$AIC == min(Firm5_besthit_AICs$AIC)), "ID"])

Firm5_best_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/otu_table.Firm5_core.",
                                                              Firm5_best_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Firm5_best_num_strain_best_fit_abun <- read.table(file = Firm5_best_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Firm5_best_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```


### Pandora (no structural)
```{r Firm5_pandora_no.struct_abun}
Firm5_pandora.nostruct_num_strain_best_fit <- as.character(Firm5_pandora.nostruct_AICs[which(Firm5_pandora.nostruct_AICs$AIC == min(Firm5_pandora.nostruct_AICs$AIC)), "ID"])

Firm5_pandora.nostruct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/otu_table.Firm5_core_no.struct.",
                                                              Firm5_pandora.nostruct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Firm5_pandora.nostruct_num_strain_best_fit_abun <- read.table(file = Firm5_pandora.nostruct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Firm5_pandora.nostruct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```

### Pandora (with structural)
```{r Firm5_pandora_struct_abun}
Firm5_pandora.struct_num_strain_best_fit <- as.character(Firm5_pandora.struct_AICs[which(Firm5_pandora.struct_AICs$AIC == min(Firm5_pandora.struct_AICs$AIC)), "ID"])

Firm5_pandora.struct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct/otu_table.Firm5_core.",
                                                              Firm5_pandora.struct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Firm5_pandora.struct_num_strain_best_fit_abun <- read.table(file = Firm5_pandora.struct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Firm5_pandora.struct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```



# Gilliamella {.tabset}

## AIC distribution

```{r Gilliamella_basic_AICs}

Gilliamella_besthit_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/Gilliamella_core.strain_fit_summary_more_resources.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Gilliamella_besthit_AICs$Datatype <- "besthit"


Gilliamella_pandora.nostruct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/Gilliamella_core_no.struct.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Gilliamella_pandora.nostruct_AICs$Datatype <- "pandora.nostruct"


Gilliamella_pandora.struct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct//Gilliamella_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Gilliamella_pandora.struct_AICs$Datatype <- "pandora.struct"


Gilliamella_besthit_AICs_plot <- ggplot(data = Gilliamella_besthit_AICs, aes(x = ID, y = AIC)) +
                                            geom_point() +
                                            theme_bw() +
                                            xlab("Number of strains") +
                                            ggtitle("Best-hit")

Gilliamella_pandora.nostruct_AICs_plot <- ggplot(data = Gilliamella_pandora.nostruct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (no structural)")


Gilliamella_pandora.struct_AICs_plot <- ggplot(data = Gilliamella_pandora.struct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (with structural)")

plot_grid(Gilliamella_besthit_AICs_plot, Gilliamella_pandora.nostruct_AICs_plot, Gilliamella_pandora.struct_AICs_plot, nrow = 1)
```


## Strain abundances {.tabset}

### Best-hit
```{r Gilliamella_besthit_abun}
Gilliamella_best_num_strain_best_fit <- as.character(Gilliamella_besthit_AICs[which(Gilliamella_besthit_AICs$AIC == min(Gilliamella_besthit_AICs$AIC)), "ID"])

Gilliamella_best_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/otu_table.Gilliamella_core.",
                                                              Gilliamella_best_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Gilliamella_best_num_strain_best_fit_abun <- read.table(file = Gilliamella_best_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Gilliamella_best_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```


### Pandora (no structural)
```{r Gilliamella_pandora_no.struct_abun}
Gilliamella_pandora.nostruct_num_strain_best_fit <- as.character(Gilliamella_pandora.nostruct_AICs[which(Gilliamella_pandora.nostruct_AICs$AIC == min(Gilliamella_pandora.nostruct_AICs$AIC)), "ID"])

Gilliamella_pandora.nostruct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/otu_table.Gilliamella_core_no.struct.",
                                                              Gilliamella_pandora.nostruct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Gilliamella_pandora.nostruct_num_strain_best_fit_abun <- read.table(file = Gilliamella_pandora.nostruct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Gilliamella_pandora.nostruct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```

### Pandora (with structural)
```{r Gilliamella_pandora_struct_abun}
Gilliamella_pandora.struct_num_strain_best_fit <- as.character(Gilliamella_pandora.struct_AICs[which(Gilliamella_pandora.struct_AICs$AIC == min(Gilliamella_pandora.struct_AICs$AIC)), "ID"])

Gilliamella_pandora.struct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct/otu_table.Gilliamella_core.",
                                                              Gilliamella_pandora.struct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Gilliamella_pandora.struct_num_strain_best_fit_abun <- read.table(file = Gilliamella_pandora.struct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Gilliamella_pandora.struct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```

# Snodgrassella {.tabset}

## AIC distribution

```{r Snodgrassella_basic_AICs}

Snodgrassella_besthit_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/Snodgrassella_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Snodgrassella_besthit_AICs$Datatype <- "besthit"


Snodgrassella_pandora.nostruct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/Snodgrassella_core_no.struct.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Snodgrassella_pandora.nostruct_AICs$Datatype <- "pandora.nostruct"


Snodgrassella_pandora.struct_AICs <- read.table("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct//Snodgrassella_core.strain_fit_summary.tsv",
                                     header = TRUE, sep = "\t", stringsAsFactors = FALSE)
Snodgrassella_pandora.struct_AICs$Datatype <- "pandora.struct"


Snodgrassella_besthit_AICs_plot <- ggplot(data = Snodgrassella_besthit_AICs, aes(x = ID, y = AIC)) +
                                            geom_point() +
                                            theme_bw() +
                                            xlab("Number of strains") +
                                            ggtitle("Best-hit")

Snodgrassella_pandora.nostruct_AICs_plot <- ggplot(data = Snodgrassella_pandora.nostruct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (no structural)")


Snodgrassella_pandora.struct_AICs_plot <- ggplot(data = Snodgrassella_pandora.struct_AICs, aes(x = ID, y = AIC)) +
                                                      geom_point() +
                                                      theme_bw() +
                                                      xlab("Number of strains") +
                                                      ggtitle("Pandora (with structural)")

plot_grid(Snodgrassella_besthit_AICs_plot, Snodgrassella_pandora.nostruct_AICs_plot, Snodgrassella_pandora.struct_AICs_plot, nrow = 1)
```


## Strain abundances {.tabset}

### Best-hit
```{r Snodgrassella_besthit_abun}
Snodgrassella_best_num_strain_best_fit <- as.character(Snodgrassella_besthit_AICs[which(Snodgrassella_besthit_AICs$AIC == min(Snodgrassella_besthit_AICs$AIC)), "ID"])

Snodgrassella_best_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/besthit/otu_table.Snodgrassella_core.",
                                                              Snodgrassella_best_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Snodgrassella_best_num_strain_best_fit_abun <- read.table(file = Snodgrassella_best_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Snodgrassella_best_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```


### Pandora (no structural)
```{r Snodgrassella_pandora_no.struct_abun}
Snodgrassella_pandora.nostruct_num_strain_best_fit <- as.character(Snodgrassella_pandora.nostruct_AICs[which(Snodgrassella_pandora.nostruct_AICs$AIC == min(Snodgrassella_pandora.nostruct_AICs$AIC)), "ID"])

Snodgrassella_pandora.nostruct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_no_struct/otu_table.Snodgrassella_core_no.struct.",
                                                              Snodgrassella_pandora.nostruct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Snodgrassella_pandora.nostruct_num_strain_best_fit_abun <- read.table(file = Snodgrassella_pandora.nostruct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Snodgrassella_pandora.nostruct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```

### Pandora (with structural)
```{r Snodgrassella_pandora_struct_abun}
Snodgrassella_pandora.struct_num_strain_best_fit <- as.character(Snodgrassella_pandora.struct_AICs[which(Snodgrassella_pandora.struct_AICs$AIC == min(Snodgrassella_pandora.struct_AICs$AIC)), "ID"])

Snodgrassella_pandora.struct_num_strain_best_fit_abun_path <- paste("/data1/gdouglas/projects/honey_bee/combined_Ellegaard.2019.2020/StrainFinder_running/core_genes_output/pandora_prepped_w_struct/otu_table.Snodgrassella_core.",
                                                              Snodgrassella_pandora.struct_num_strain_best_fit,
                                                              ".txt",
                                                              sep = "")

Snodgrassella_pandora.struct_num_strain_best_fit_abun <- read.table(file = Snodgrassella_pandora.struct_num_strain_best_fit_abun_path,
                                                              header = FALSE, sep = "\t", skip = 1)

Heatmap(log(as.matrix(Snodgrassella_pandora.struct_num_strain_best_fit_abun +  1e-08)),
        show_column_names = FALSE,
        column_title = "Strains",
        row_title = "Samples",
        heatmap_legend_param = list(title = "log(abun \n      + 1e-8)"))
```



# Session info {.tabset}

## Hide session info

## Show session info

Session details printed out for reproducibility.

```{r session_info}
sessionInfo()
```
